---
title: "TwitterBuzz"
author: "Anees Parwez"
date: "1/26/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Loading Data:
```{r}
Data=read.table("C:\\Users\\SHAHID\\Desktop\\Academic\\M-Sem1\\Project and Assinment\\Re Tec\\Twitter Buzz\\Twitter\\Twitter_data.txt",header=FALSE,sep=",")
```

For interpretation of traits, it is important we identify the columns. Hence, add appropriate column names:
```{r}
variables=c("NCD","AI","AS(NA)","BL","NAC","AS(NAC)","CS","AT","NA","ADL","NAD")
for(k in 1:11){
  for(j in 1: 7){
    names(Data)[7*(k-1)+j]=paste(variables[k],j%%7,sep="")
  }
    names(Data)[7*k]=paste(variables[k],7,sep="")
}
names(Data)[78]="Response"
names(Data)
```

The way variables are described, we sense presence of multicollinearity which we subsequently explore by scatter plots:

```{r}
library(ggplot2)
ggplot(data=Data,aes(x=NCD1,y=AI1))+ geom_point() +labs(x="NCD 1",y="AI 1") + 
 ggtitle("Counts of NCD and AI at first TimePoint")
```
```{r}
ggplot(data=Data,aes(x=NA2,y=NA3))+ geom_point() +labs(x="NA 2",y="NA 3") + 
ggtitle("Number of Author Interacting at different TimePoints")

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
